---
title       : Project Midpoint
subtitle    : Rady School of Management - MGT 444
author      : Jeff Binabio, Julian Ganguli, Andrew Lee, and Lei Su
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Data

- CMS.gov
    + Built an automated web scraper to gather MA CMS data
        + 80 zip files
        + Unzips, compiles, and outputs all data in one csv file
    + Data frame 254,566 x 12

- Other
    + Geo code data

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("~/Google Drive New/Rady (G-Drive)/MGT 444 (analytics)/KP Project/plots")
library('ggplot2')
library('googleVis')
load('plots.Rdata')
```

--- .class #id 

## Exploratory Data Analysis: County by Area Type
There are a few semi-urban and rural counties that have penetration rates well above other counties in their respective class.

```{r, fig.height=6, fig.width=13, echo=FALSE}

plot.1 + ggtitle('')

```

--- .class #id 

## Heat Map of MA Penetration Rates by CA County: Jan 2015
Facility locations are primarily in areas with high penetration rates.

```{r, cache=FALSE, fig.height=6, fig.width=14, echo=FALSE, message=FALSE, warning=FALSE}

p2 + ggtitle('')

```

--- .class #id 

## MA Penetration Rates by CA Counties by Time:<br>
## 2008 to 2015
Gradual increasing trends in larger counties. Smaller counties have mix-trend patterns.

```{r, fig.height=6, fig.width=13, echo=FALSE, message=FALSE, warning=FALSE}

plot.2 + ggtitle('')

```

--- .class #id 

## Many Dimensions to Consider...

### It would be interesting to see how each county has changed over time in several dimensions simultaneously. <br>
<br>
### Let's look at a motion chart... 

--- .class #id 

## Let's Look at a Motion Chart
In 2008, there are 3 clusters of counties. By 2015, we see 4 clusters... possibly a fifth cluster emerging.

```{r, motionchartcode, results='asis', echo=FALSE}

options(gvis.plot.tag = "chart")

plot(mo.chart.slide.one)

```

--- .class #id

## To Be Continued...

### This presentation has been truncated.
### The company specific data is included in a seperate presentation. 

--- .class #id
